---
title: "RespirationRates_analysis"
author: "Samuel Gurr"
date: "2023-10-15"
output: html_document
---

# Purpose: Oyster project 2021 - Respiration rate data 
# analysis of respiration rate data
# Written by: Sam J Gurr (last edit 10/14/2023

# load packages and working dir

```{r, setup}
# LOAD PACKAGES 
library(emmeans)
library(car)
library(ggpubr)
library(rcompanion)
library(emmeans)
library(forcats)
library(dplyr)
library(vegan)
library(tidyverse)
# SET WORKING DIRECTORY 
knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/")

```


# Load data 

```{r, load data}
Resp.Master  <- read.csv(file="Output/Respiration/RespirationMaster.csv", header=T) # reference for the respirometry data - contains the 'Chamber_Tank' for each sensor channel (whether an animal or a blank)

```

(1) 'APRIL' as 24 hours post ferilization

* call the data
```{r, 24 HPF call data}
# model effect of treatment on resp rate 20210430
Resp_APRIL <- Resp.Master %>% 
  dplyr::filter(Date %in% '4/30/2021') # %>% 
Resp_APRIL # view the data
# View(Resp_APRIL)
```

* Runs stats (ultimately report PERMANOVA as ANOVA assumptions are not possible here)
```{r, 24 HPF run da mod}

# Three way ANOVA 
LMmod.APRIL   <- aov(lm(resp_ng_L_indiv_hr~Temp*pCO2*Salinity,data=Resp_APRIL))
shapiro.test(residuals(LMmod.APRIL)) # 0.009733 - non normal
leveneTest(LMmod.APRIL) # 0.3256 - variance okay
summary(LMmod.APRIL)

# PERMANOVA - Resp_APRIL mltvariate anova 
RR_metadata           <- Resp_APRIL %>% dplyr::select(Temp,pCO2,Salinity,Chamber_tank) %>% dplyr::rename(sample.id = Chamber_tank) # all but the DV - only IVs
RR_metadata$sample.id <- as.character(RR_metadata$sample.id)
RR_data               <- Resp_APRIL[, 'resp_ng_L_indiv_hr', drop = FALSE]
RR_distance_euc       <- vegdist(RR_data, "euclidean")
RR_distance_mtx           <- as.matrix(RR_distance_euc)
rownames(RR_distance_mtx) <- Resp_APRIL$Chamber_tank
colnames(RR_distance_mtx) <- Resp_APRIL$Chamber_tank
RR_distance               <- tibble::rownames_to_column(as.data.frame(RR_distance_mtx), "sample.id")
RR_meta_distance          <- inner_join(RR_metadata,RR_distance, by = "sample.id")
RR_dist                   <- RR_meta_distance  %>% dplyr::select(all_of(RR_meta_distance$sample.id)) %>% as.dist() 
adonis_run                <- adonis2(RR_dist  ~ pCO2*Temp*Salinity, data=RR_meta_distance, perms = 1000) 
adonis_run
#                    Df SumOfSqs      R2      F Pr(>F)  
# pCO2                1    0.473 0.00890 0.2310  0.683  
# Temp                1    4.663 0.08773 2.2771  0.140  
# Salinity            1    4.786 0.09005 2.3371  0.125  
# pCO2:Temp           1    8.265 0.15549 4.0357  0.049 *
# pCO2:Salinity       1    0.442 0.00832 0.2159  0.658  
# Temp:Salinity       1    0.671 0.01261 0.3274  0.610  
# pCO2:Temp:Salinity  1    1.086 0.02044 0.5305  0.497  
# Residual           16   32.768 0.61646                
# Total              23   53.156 1.00000

# POSTHOC PERMANOVA proptocol - run the four treatment combinations 
# CRE AN OA_SALINITY COLUMNATE
RR_meta_distance  <- RR_meta_distance %>% dplyr::mutate(pCO2_Temp = paste0(pCO2,' x ',Temp))
# TRUNCATE THE DATA FOR EACH PAIR BASED ON OA AND SALINITY, WITH UNIQUE TITLE
# Note: two two-factor variables == 6 possible pairs 
# METADATA (IV)
RR_HH_LL_metadata <- RR_meta_distance %>% dplyr::filter(pCO2_Temp %in% c('H x H', 'L x L'))
RR_HH_LH_metadata <- RR_meta_distance %>% dplyr::filter(pCO2_Temp %in% c('H x H', 'L x H'))
RR_HH_HL_metadata <- RR_meta_distance %>% dplyr::filter(pCO2_Temp %in% c('H x H', 'H x L'))
RR_HL_LH_metadata <- RR_meta_distance %>% dplyr::filter(pCO2_Temp %in% c('H x L', 'L x H'))
RR_HL_LL_metadata <- RR_meta_distance %>% dplyr::filter(pCO2_Temp %in% c('H x L', 'L x L'))
RR_LH_LL_metadata <- RR_meta_distance %>% dplyr::filter(pCO2_Temp %in% c('L x H', 'L x L'))
# DISTANCE (DV)
RR_HH_LL_dist     <- RR_meta_distance %>% 
  dplyr::filter(sample.id %in% RR_HH_LL_metadata$sample.id) %>% 
  dplyr::select(RR_HH_LL_metadata$sample.id) %>% 
  as.dist() 
RR_HH_LH_dist     <- RR_meta_distance %>% 
  dplyr::filter(sample.id %in% RR_HH_LH_metadata$sample.id) %>% 
  dplyr::select(RR_HH_LH_metadata$sample.id) %>% 
  as.dist() 
RR_HH_HL_dist     <- RR_meta_distance %>% 
  dplyr::filter(sample.id %in% RR_HH_HL_metadata$sample.id) %>% 
  dplyr::select(RR_HH_HL_metadata$sample.id) %>% 
  as.dist() 
RR_HL_LH_dist     <- RR_meta_distance %>% 
  dplyr::filter(sample.id %in% RR_HL_LH_metadata$sample.id) %>% 
  dplyr::select(RR_HL_LH_metadata$sample.id) %>% 
  as.dist() 
RR_HL_LL_dist     <- RR_meta_distance %>% 
  dplyr::filter(sample.id %in% RR_HL_LL_metadata$sample.id) %>% 
  dplyr::select(RR_HL_LL_metadata$sample.id) %>% 
  as.dist() 
RR_LH_LL_dist     <- RR_meta_distance %>% 
  dplyr::filter(sample.id %in% RR_LH_LL_metadata$sample.id) %>% 
  dplyr::select(RR_LH_LL_metadata$sample.id) %>% 
  as.dist()

# RUN ADONIS FOR EACH PAIR
RR_adonis_HH_LL   <- adonis2(RR_HH_LL_dist  ~ pCO2_Temp, data=RR_HH_LL_metadata, perms = permutations) # nope
RR_adonis_HH_LH   <- adonis2(RR_HH_LH_dist  ~ pCO2_Temp, data=RR_HH_LH_metadata, perms = permutations) # yup
RR_adonis_HH_HL   <- adonis2(RR_HH_HL_dist  ~ pCO2_Temp, data=RR_HH_HL_metadata, perms = permutations) # nope
RR_adonis_HL_LH   <- adonis2(RR_HL_LH_dist  ~ pCO2_Temp, data=RR_HL_LH_metadata, perms = permutations) # yup
RR_adonis_HL_LL   <- adonis2(RR_HL_LL_dist  ~ pCO2_Temp, data=RR_HL_LL_metadata, perms = permutations) # nope
RR_adonis_LH_LL   <- adonis2(RR_LH_LL_dist  ~ pCO2_Temp, data=RR_LH_LL_metadata, perms = permutations) # yup

# Summary table to report mean se data and percent differences
# main effect of temperature 
Resp_APRIL %>% 
  group_by(Temp) %>% 
  summarise_each(funs(mean, sd, se=sd(.)/sqrt(n())),resp_ng_L_indiv_hr)


# Temp  mean  sd        se
# H	0.6335014	1.076005	0.3106158	
# L	1.5151186	1.802943	0.5204648	

((1.5151186-0.6335014)/1.5151186)*100 # 58.188

# post hoc interaction term 
Resp_APRIL %>% 
  dplyr::mutate(Temp_pCO2 = paste(Temp,pCO2, sep = '')) %>% 
  group_by(Temp_pCO2) %>% 
  summarise_each(funs(mean, sd, se=sd(.)/sqrt(n())),resp_ng_L_indiv_hr)

# Temp_pCO2 mean      sd          se
# HH	      1.0799260	1.43531100	0.58596326	
# HL	      0.1870767	0.09329505	0.03808755	
# LH	      0.7878666	0.95776865	0.39100741	
# LL	      2.2423705	2.22815140	0.90963900

((2.2423705-0.1870767)/2.2423705)*100 # 91.65719
((0.7878666-0.1870767)/0.7878666)*100 # 76.25528


Age1_RR_MeanSE <- ggplot(data=Resp_APRIL, 
                             aes(x=fct_relevel(Salinity, c("L", "H")), 
                                 y=resp_ng_L_indiv_hr, 
                                 colour=fct_relevel(pCO2, c("H", "L")), 
                                 linetype= fct_relevel(Temp, c("L", "H")))) +
                             scale_linetype_manual(breaks=c("L", "H"), values=c("dashed","solid")) +
                             scale_colour_manual(breaks=c("L", "H"), values=c("#56B4E9","#E69F00")) +
                             geom_point(aes(colour = fct_relevel(pCO2, c("H", "L"))), 
                                        position = position_dodge2(width = 0.75)) + 
                             stat_summary(fun.y="mean", size = 0.8,
                                          position = position_dodge2(width = 1)) +
                             stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                          fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                          geom = 'errorbar', 
                                          position = position_dodge2(width = 1)) +
                              labs(title="Age = 24 hours", x ="Salinity", y = "Larvae RR (ng L-1 indiv-1 hr-1)") +
                              theme_classic() +
                              theme(panel.grid.major = element_blank(), 
                                    panel.grid.minor = element_blank(), 
                                    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
                                    axis.text=element_text(size=12),
                                    legend.position="none")

Age1_RR_MeanSE

# save the plot 
setwd("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis")
pdf("Output/Respiration/Day1_MeanSE.pdf", width=8, height=6)
print(Age1_RR_Boxplot)
dev.off()



```

* plot a guy 

```{r, plots plots plots!}

APRIL_all <- Resp_APRIL %>%
                  dplyr::mutate(Temp_pCO2 = paste(Temp,pCO2, sep = '')) %>% 
                  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
                  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                                            "LHL", "LHH", "HHL",'HHH',
                                            "LLL", "LLH", "HLL", 'HLH')) %>%
                  ggplot(aes(fct_relevel(Temp_pCO2, c("LH", "HH", "LL", "HL")), # x 
                             resp_ng_L_indiv_hr,
                             fill = factor(Salinity)) ) +
                        scale_fill_manual(values=c("white", "grey10")) +
                        geom_boxplot(size=0.2, alpha=0.1) +
                        geom_point(aes(shape=Salinity),
                               size = 2, 
                               position = position_jitterdodge(jitter.width = 0.5)) +
                        labs(title = "C virginica, 24 hr larvae", 
                             y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
                             x = "Temp_pCO2_Salinity") + 
                        scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                        annotate("text", x=4, y=0.8, label = "c (1.3 medArag)", size  =3) +
                        annotate("text", x=2, y=3, label = "ab (0.54 medArag)", size =3) +
                        annotate("text", x=1, y=3, label = "b (0.45 medArag)", size  =3) +
                        annotate("text", x=3, y=5, label = "a (1.03 medArag)", size  =3) +
                        #annotate("rect", xmin = 0, xmax = 4.5, ymin = 0, ymax = 6.5,alpha = .2) +
                        theme_classic() 

APRIL_all

pdf("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/Respiration/Day1_RR_posthoc.pdf", width=8, height=6)
print(APRIL_all)
dev.off()

APRIL_all <- Resp_APRIL %>%
                  dplyr::mutate(Temp_pCO2 = paste(Temp,pCO2, sep = '')) %>% 
                  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
                  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                                            "LHL", "LHH", "HHL",'HHH',
                                            "LLL", "LLH", "HLL", 'HLH')) %>%
                  ggplot(aes(fct_relevel(Temp_pCO2, c("LH", "HH", "LL", "HL")), # x 
                             resp_ng_L_indiv_hr,
                             fill = factor(Salinity)) ) +
                        scale_fill_manual(values=c("white", "grey10")) +
                        geom_boxplot(size=0.2, alpha=0.1) +
                        geom_point(aes(shape=Salinity),
                               size = 2, 
                               position = position_jitterdodge(jitter.width = 0.5)) +
                        labs(title = "C virginica, 24 hr larvae", 
                             y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
                             x = "Temp_pCO2_Salinity") + 
                        scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                        annotate("text", x=4, y=0.8, label = "c (1.3 medArag)", size  =3) +
                        annotate("text", x=2, y=3, label = "ab (0.54 medArag)", size =3) +
                        annotate("text", x=1, y=3, label = "b (0.45 medArag)", size  =3) +
                        annotate("text", x=3, y=5, label = "a (1.03 medArag)", size  =3) +
                        #annotate("rect", xmin = 0, xmax = 4.5, ymin = 0, ymax = 6.5,alpha = .2) +
                        theme_classic() 



APRIL_all_MEANSe <- Resp_APRIL %>%
  dplyr::mutate(Temp_pCO2 = paste(Temp,pCO2, sep = '')) %>% 
  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                                            "LHL", "LHH", "HHL",'HHH',
                                            "LLL", "LLH", "HLL", 'HLH')) %>%
  ggplot(aes(fct_relevel(Temp_pCO2, c("LH", "HH", "LL", "HL")), # x 
                        resp_ng_L_indiv_hr,
                        fill = factor(Salinity)),
                        group= full.treatment) +
  geom_point(aes(shape = Salinity, group= full.treatment),
             size =2,
             position = position_jitterdodge(jitter.width = 0.5)) +
  stat_summary(aes(group= full.treatment),
               fun = mean, 
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               geom = 'errorbar',  width = 0.25,
               position = position_jitterdodge(jitter.width = 0.5)) +
  stat_summary(aes(group= full.treatment),
               fun = mean, fun.min = mean, fun.max = mean,
               geom = 'point',  size = 5, shape = 20, color = "red",
               position = position_jitterdodge(jitter.width = 0.5)) +
  # scale_y_continuous(limits = c(0, 30)) +
  # scale_shape_manual(values = c(16, 15)) +
  # labs(x = '', y = '') +
  scale_shape_manual(values = c(16, 15)) +
  scale_fill_manual(values=c("white", "grey10")) +
                        labs(title = "C virginica, 24 hr larvae", 
                             y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
                             x = "Temp_pCO2_Salinity") + 
                        scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                        annotate("text", x=4, y=0.8, label = "c (1.3 medArag)", size  =3) +
                        annotate("text", x=2, y=3, label = "ab (0.54 medArag)", size =3) +
                        annotate("text", x=1, y=3, label = "b (0.45 medArag)", size  =3) +
                        annotate("text", x=3, y=5, label = "a (1.03 medArag)", size  =3) +
                        #annotate("rect", xmin = 0, xmax = 4.5, ymin = 0, ymax = 6.5,alpha = .2) +
                        theme_classic() 



pdf("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/Respiration/Day1_RR_posthoc_meanse.pdf", width=8, height=6)
print(APRIL_all_MEANSe)
dev.off()


```


```{r, temp by CO2 post hoc plot}

APRIL_TemppCO2 <- Resp_APRIL %>%
                    dplyr::mutate(Temp_pCO2 = 
                                    paste0(Temp,pCO2, sep = '')) %>% 
                    ggplot(aes(fct_relevel(Temp_pCO2, c("LH", "HH", "LL", "HL")), # x 
                               resp_ng_L_indiv_hr,  # y
                               group = factor(Temp_pCO2)) ) +
                    geom_boxplot(size=0.2, alpha=0.1) +
                    geom_point(aes(shape=Salinity),
                               size = 2, 
                               position = position_jitterdodge(jitter.width = 0.5)) +
                    # scale_fill_manual(values=c("white", "grey40")) +
                    labs(title = "C virginica, 24 hr larvae", 
                         y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
                         x = "Temp_pCO2") + 
                    annotate("text", x=3.8, y=0.8, label = "c (1.3 medArag)", size  =3) +
                    annotate("text", x=1.8, y=1.2, label = "ab (0.54 medArag)", size =3) +
                    annotate("text", x=0.8, y=1.2, label = "b (0.45 medArag)", size  =3) +
                    annotate("text", x=2.8, y=3.2, label = "a (1.03 medArag)", size  =3) +
                    #annotate("rect", xmin = 0, xmax = 4.5, ymin = 0, ymax = 6.5,alpha = .2) +
                    theme_classic() 

APRIL_TemppCO2




```



```{r, heatplot}
library(tidyr)
Resp_means_APRIL <- Resp_APRIL %>% 
  dplyr::mutate(Age = "24 hrs") %>% 
  na.omit() %>% 
  # dplyr::group_by(Temp, pCO2, Salinity, Age) %>% # group by all - NO interaction!
  dplyr::group_by(Temp, pCO2, Age) %>% # group by temp and pCO2 - YES interaction!
  dplyr::summarise(mean_RR = mean(resp_ng_L_indiv_hr), 
                   n       = n(),
                   sd_RR   = sd(resp_ng_L_indiv_hr),
                   se_RR   = sd_RR/(sqrt(n)))


# APRIL_MeanSE <- Resp_means_APRIL %>%
#   dplyr::mutate(Temp_pCO2 = paste(Temp,pCO2, sep = '_')) %>% 
#   ggplot(aes(Temp_pCO2, mean_RR , fill = factor(Salinity))) +
#   geom_errorbar(aes(ymin = mean_RR - se_RR, 
#                     ymax = mean_RR + se_RR), 
#                 width = 0.5, 
#                 position= "dodge2") +
#   geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1))+
#   scale_fill_manual(values=c("white", "grey40")) +
#   labs(title = "C virginica, 24 hr larvae", 
#        y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
#        x = "Temp_pCO2") + 
#   theme_classic() 
# APRIL_MeanSE

Heatplot_RR_APRIL <- Resp_means_APRIL %>% 
                        dplyr::mutate(Temp_pCO2 = (paste(Temp, pCO2,sep=''))) %>% 
                        # dplyr::mutate(OA_Sal = (paste(pCO2, Salinity,sep=''))) %>% 
                        ggplot(aes(x = as.factor(Age),
                                   y = mean_RR)) +
                                   #shape = stage)) + 
                        geom_rect(aes(fill = mean_RR), 
                                  xmin = -Inf, 
                                  xmax = Inf, 
                                  ymin = -Inf, 
                                  ymax = Inf, 
                                  alpha = 0.3) +
                        geom_point(color = 'black') +
                        geom_errorbar(aes(ymin = mean_RR - se_RR, 
                                          ymax = mean_RR + se_RR), 
                                      width = 0.5, 
                                      position= "dodge2") +
                        theme_bw() +  
                        theme(panel.grid.major = element_blank(),
                              panel.grid.minor = element_blank()) +
                        # facet_grid(vars(Temp), 
                                   # vars(fct_relevel(OA_Sal, c("HL", "LL", "HH", "LH")))) +
                        facet_grid(vars(Temp),
                                   vars(fct_relevel(Temp_pCO2, c("HL", "LL", "HH", "LH")))) +
                        scale_fill_gradient(low = "orange", 
                                            high = "forestgreen", 
                                            aesthetics = "fill")

Heatplot_RR_APRIL
# 
# setwd("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/")
# pdf("Respiration/Day1_RR_heatplot.pdf", width=8, height=6)
# print(Heatplot_RR_APRIL)
# dev.off()


# setwd("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/")
# pdf("Respiration/Day1_RR_posthoc.pdf", width=8, height=6)
# print(APRIL_MeanSE)
# dev.off()


```


# MAY - 8 days post fertilization---------------------------------------------------------- #


```{r}
# model effect of treatment on resp rate 20210507
Resp_MAY <- Resp.Master %>% 
  dplyr::filter(Date %in% '5/7/2021')  %>% 
  dplyr::mutate(Age = '8days') 

  
Resp_MAY # view the data
```

```{r}
# Three way ANOVA 
LMmod.MAY   <- aov(lm(resp_ng_L_indiv_hr~Temp*pCO2*Salinity,data=Resp_MAY))
shapiro.test(residuals(LMmod.MAY)) # 0.006028
leveneTest(LMmod.MAY) # 0.764 good
summary(LMmod.MAY)
# log transformation
LMmod.MAY_T   <- aov(lm(log(resp_ng_L_indiv_hr)~Temp*pCO2*Salinity,data=Resp_MAY))
shapiro.test(residuals(LMmod.MAY_T)) # 0.7608
leveneTest(LMmod.MAY_T) # 0.8419 good
summary(LMmod.MAY_T)
# Df Sum Sq Mean Sq F value Pr(>F)  
# Temp           1  3.355   3.355   3.544 0.0924 .
# pCO2           1  0.972   0.972   1.027 0.3373  
# Salinity       1  3.664   3.664   3.870 0.0807 .
# Temp:pCO2      1  3.794   3.794   4.008 0.0763 .
# Temp:Salinity  1  0.022   0.022   0.023 0.8825  
# pCO2:Salinity  1  0.117   0.117   0.123 0.7334  
# Residuals      9  8.521   0.947

```

```{r}
# Figures
Resp_MAY_select  <- Resp_MAY %>% 
  dplyr::select(c('resp_ng_L_indiv_hr', 'Temp', 'pCO2', 'Salinity')) %>% 
  dplyr::mutate(Age = '8days')


May_all <- Resp_MAY_select %>%
                  dplyr::mutate(Temp_pCO2 = paste(Temp,pCO2, sep = '')) %>% 
                  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
                  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                                            "LHL", "LHH", "HHL",'HHH',
                                            "LLL", "LLH", "HLL", 'HLH')) %>%
                  ggplot(aes(fct_relevel(Temp_pCO2, c("LH", "HH", "LL", "HL")), # x 
                             resp_ng_L_indiv_hr,
                             fill = factor(Salinity)) ) +
                        scale_fill_manual(values=c("white", "grey10")) +
                        geom_boxplot(size=0.2, alpha=0.1) +
                        geom_point(aes(shape=Salinity),
                               size = 2, 
                               position = position_jitterdodge(jitter.width = 0.5)) +
                        labs(title = "C virginica, 8 day larvae", 
                             y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
                             x = "Temp_pCO2") + 
                        scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                        theme_classic() 

May_all

setwd("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/")
pdf("Respiration/Day8_RR.pdf", width=8, height=6)
print(May_all)
dev.off()

```
Resp_means_MAY <- Resp_MAY_select %>% 
  na.omit() %>% 
  dplyr::group_by(Temp, pCO2, Salinity, Age) %>% 
  dplyr::summarise(mean_RR = mean(resp_ng_L_indiv_hr), 
                   n       = n(),
                   sd_RR   = sd(resp_ng_L_indiv_hr),
                   se_RR   = sd_RR/(sqrt(n)))


Heatplot_RR_MAY <- Resp_means_MAY %>% 
  dplyr::mutate(OA_Sal = (paste(pCO2, Salinity,sep=''))) %>% 
  ggplot(aes(x = as.factor(Age),
             y = mean_RR)) +
  #shape = stage)) + 
  geom_rect(aes(fill = mean_RR), 
            xmin = -Inf, 
            xmax = Inf, 
            ymin = -Inf, 
            ymax = Inf, 
            alpha = 0.3) +
  geom_point(color = 'black') +
  geom_errorbar(aes(ymin = mean_RR - se_RR, 
                    ymax = mean_RR + se_RR), 
                width = 0.5, 
                position= "dodge2") +
  theme_bw() +  
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  facet_grid(vars(Temp), 
             vars(fct_relevel(OA_Sal, c("HL", "LL", "HH", "LH")))) +
  scale_fill_gradient(low = "orange", 
                      high = "forestgreen", 
                      aesthetics = "fill")

setwd("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/")
pdf("Respiration/Day8_RR_heatplot.pdf", width=8, height=6)
print(Heatplot_RR_MAY)
dev.off()


