---
title: "resp_calc_analysis_RMD"
author: "Samuel Gurr"
date: "9/22/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r load packages + set wd + load data + ready data, include=FALSE}
# Purpose: Oyster project 2021 - Respiration rate data 
# analysis of respiration rate data
# Written by: Sam J Gurr (last edit 9/14/2021)

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(reshape2)
library(lme4)
library(lmerTest)
library(performance) # check check_model QC 
library(see)
library(patchwork)
library(forcats)
library(lawstat)
library(car)

# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

setwd("C:/Users/samjg/Documents/Github_repositories/Cvriginica_multistressor/RAnalysis") # personal computer
# setwd("C:/Users/samuel.gurr/Documents/Github_repositories/Cvriginica_multistressor/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

exp_metadata <- read.csv(file="Data/ExperimentMetadata.csv", header=T) # treatment assignments to 'Chamber_Tank'

aragonite_dat<- read.csv(file='Output/Water_Chem/Chem.Table_sep.csv', header = T) %>% 
  dplyr::select(c('meanAragonite','Temp_OA_Sal')) %>%  
  dplyr::rename(TempCarbSal = Temp_OA_Sal)
aragonite_dat$TempCarbSal <-  gsub("_", "", aragonite_dat$TempCarbSal)

counts_resp  <- read.csv(file="Data/Counts_resp.csv", header=T) # reference for the respirometry data - contains the 'Chamber_Tank' for each sensor channel (whether an animal or a blank)
resp.ref     <- read.csv(file="Data/Respiration/Reference_master.csv", header=T) %>% 
  dplyr::filter(!Filename %in% c('1_3_19_21_raw.txt', 'may_7_2021_low_temo_10-12_ans_13-15_high_sal_raw_b.txt')) # reference for the respirometry data - contains the 'Chamber_Tank' for each sensor channel (whether an animal or a blank)
resp.data    <- read.csv(file="Output/Respiration/Cumulative_resp_alpha0.4.csv", header=T) %>% 
  dplyr::filter(!Filename %in% c('1_3_19_21_raw.txt', 'may_7_2021_low_temo_10-12_ans_13-15_high_sal_raw_b.txt'))# read the calculated raw rates from 'resp_LoLin' script - contains the calculated rate (not normalized for blanks) for each sensor-channel

# merge the exp_metadata with the resp.data
resp.ref_merged                 <- merge(exp_metadata, resp.ref, by = 'Chamber_tank', all=TRUE) # all TRUE allows us to keep the blanks
resp.data_merged                <- merge(resp.data, resp.ref_merged, by = c('Date', 'Channel','Notes','Filename')) # out master file moving forward....
resp.data_merged$TempCarbSal    <- paste(resp.data_merged$Temp, resp.data_merged$pCO2, resp.data_merged$Salinity, sep ='')
```



### CALCULATE RESPIRATION RATES
(1) summary table of blanks to normalize respiration rates
  - we will use 'Lpc' value (or L%) was chosen to generally choose the local regression with the majority of observations in the truly linear subset of data
  - review Olito et al. 2017 Estimating monotonic rates from biological data using local linear regression
  
  
```{r blanks, echo=FALSE}

dates.runs <- resp.data_merged %>%  # call table
  dplyr::distinct(Date, Notes) # call all unique values for date run and sw condition
dates.runs <- na.omit(dates.runs)
# call dataframe and build table to rbind in for loop
blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Notes', 'BLANK.mean.Lpc', 'BLANK.mean.Leq' , 'BLANK.mean.Lz') # names for comuns in the for loop

# for loop. objective = obtian a mean value for all blanks specific to date, run #, seawater treatment
for(i in 1:nrow(dates.runs)) {
  data <- resp.data_merged %>% 
    dplyr::select(Date, Chamber_tank, Notes, Lpc,  Leq, Lz) %>% 
    dplyr::filter(!is.na(Lpc)) %>% # ommits empty resp channels (if any)
    dplyr::filter(Notes == dates.runs[i,2])
  
  blanks <- data %>%
    dplyr::filter(Chamber_tank == "blank") %>% 
    dplyr::summarise(mean_Lpc = mean(abs(Lpc)),
                     mean_Leq = mean(abs(Leq)), 
                     mean_Lz = mean(abs(Lz)))
  
  blanks.table$Date           <- dates.runs[i,1] # all files have date in the form of yyyymmdd at the start of each csv name
  #blanks.table$RUN <- dates.runs[i,2] # assign the run to the number in the title for the trials completed that day
  blanks.table$Notes      <- dates.runs[i,2]
  blanks.table$BLANK.mean.Lpc <- blanks[1,1]
  blanks.table$BLANK.mean.Leq <- blanks[1,2]
  blanks.table$BLANK.mean.Lz  <- blanks[1,3]
  # blanks.table$alpha <- data[1,9] # set at start of script - reresents the proportion of data for final estimate of slopes (Lpc, Leq, Lz)
  
  df <- data.frame(blanks.table) # name dataframe for this singl e row
  blanks_total <- rbind(blanks_total,df) #bind to a cumulative list dataframe
  # print(blanks_total) # print to monitor progress
}

head(blanks_total) # view blanks table
```



(2) Calculate respiration rates as ng O2 L-1 indiv-1 hr-1
  - normalize by mean value of blanks for each treatment, grouped by 'Date' and 'Notes' (as the run wihtin day)
  - omit rows resprenting blank resp > sample resp - likely bad data, view to troubleshoot if needed
  
  
```{r normalize resp rates by blanks, echo=FALSE}
Resp.blanks.merge <- merge(resp.data_merged, blanks_total, by=c("Date", "Notes")) %>% # NOTE: this repeats for every distinct length value
  dplyr::filter(!Chamber_tank =='blank') %>% 
  dplyr::mutate(resp_norm = Lpc - BLANK.mean.Lpc) # calc resp norm - note Lpc is still raw data  - thus a positive resp norm means blank > sample resp - bad data! 

Resp.blanks.merge_OM <- Resp.blanks.merge %>% dplyr::filter(!resp_norm > 0)  # omits respiration rate values showing an increase in O2 over time 
Resp.outliers <- Resp.blanks.merge_OM %>% dplyr::filter(resp_norm > 0)  # lets lopok at this data - possible troubleshootiung to ID these outliers...
print(c("number of blank resp > sample resp =",nrow(Resp.outliers)))

count_check <- Resp.blanks.merge_OM %>% dplyr::group_by(Date,TempCarbSal) %>% dplyr::summarise(n = n())
count_check
```

- calculate resp rates
  
```{r calc as resp_ng_L_indiv_hr, echo=FALSE}
vial.vol <- 0.08 # milliliters (ml)
Resp.Master <- merge(Resp.blanks.merge_OM[,c(1,3,5,9:13,17)], counts_resp[,c(1,6:7)], by = c('Date','Chamber_tank'))
Resp.Master$resp_ng_L_indiv_hr <- ( 
  ( ( (abs(Resp.Master$resp_norm)*1000000) * # call absolute value of resp in mg per minute - convert to ng min-1
      (vial.vol/1000) ) / # correct ng minute-1 to ng liter-1 by multiplying by the resp vial in liters
      Resp.Master$Counts ) * # normalize by individual or larvae count - as to ng L-1 individual-1
    (60)) # correct for the time; final value is ng Liter-1 individual-1 hour-1

# mean sd rates
# mean(Resp.Master$resp_ng_L_indiv_hr) # mean = 0.4994656
# sd(Resp.Master$resp_ng_L_indiv_hr) # sd= 0.8197345

head(Resp.Master)[,c(1:3,11)]
```


## ANALYSIS
### Day 1 Respirometry (20210430)
  - a. filter the dataset for taget data
  - b. add column for mean aragonite sat. (note: this is from the entire experiment, not just day 1 chemistry!)
  - c. run moels and diagnostics
  - d. plot (reconfigure data as needed for plotting; i.e. melt/dcast, etc.)
  
  
```{r day 1 analysis, echo=TRUE}

# a.
Resp_APRIL <- Resp.Master %>% 
  dplyr::filter(Date %in% '4/30/2021') 

# b.
Resp_APRIL <- merge(Resp_APRIL, aragonite_dat, by = 'TempCarbSal') # merge with the mean aragonite saturation state

# c.
LMmod.APRIL   <- aov(lm( resp_ng_L_indiv_hr~Temp*pCO2*Salinity,data=Resp_APRIL))
print('LM model  == aov( lm ( resp_ng_L_indiv_hr ~ Temp * pCO2 * Salinity, data = Resp_APRIL ) )')
summary(LMmod.APRIL)
check_model(LMmod.APRIL) # observe the diagnostics of the model
shapiro.test(residuals(LMmod.APRIL)) # non normal
leveneTest(LMmod.APRIL) # good

# LME model here however we do only have one rep per chamber_tank in some cases, thus the lm (above is the same)
# MEmod.APRIL    <- lmer(resp_ng_L_indiv_hr~Temp*pCO2*Salinity + (1|Chamber_tank),REML=F, data=Resp_APRIL)
# summary(MEmod.APRIL)
# check_model(MEmod.APRIL)
# shapiro.test(residuals(MEmod.APRIL)) # non normal 0.0107
# leveneTest(MEmod.APRIL) # good

# POst-hoc tests and exploration of sig effects
TukeyHSD(LMmod.APRIL, 'Temp:pCO2')


# d. 
Resp_APRIL_select  <- Resp_APRIL %>% dplyr::select(c('resp_ng_L_indiv_hr', 'Temp', 'pCO2', 'Salinity'))
Resp_APRIL_melt    <- tidyr::gather(Resp_APRIL_select, variable, value, -resp_ng_L_indiv_hr)

# MAIN EFFECT PLOT
# ggplot(Resp_APRIL_melt, aes(value , resp_ng_L_indiv_hr , fill = factor(value ))) +
#   theme(panel.grid=element_blank()) +
#   scale_color_manual(values=c("#56B4E9","#D55E00")) +
#   geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.5))+
#   geom_boxplot(size=0.2, alpha=0.1) +
#   theme_bw() +
#   facet_wrap(~variable, scales = "free_y")

# INTERACTION PLOT
Resp_APRIL %>%
  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                            "HHH", "HLH", "LHH",'LLH',
                            "HHL", "HLL", "LHL", 'LLL')) %>%
  ggplot(aes(meanAragonite, resp_ng_L_indiv_hr , group =full.treatment, fill = factor(Temp))) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.05))+
  #geom_boxplot(size=.2, alpha=0.1, width =0.2) +
  scale_fill_manual(values=c("#D55E00","#56B4E9", "#D55E00","#56B4E9", 
                             "#D55E00","#56B4E9", "#D55E00","#56B4E9")) +
  labs(title = "Respiration rates; C virginica day 1", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
       x = "Aragonite saturation") +
  annotate("text", x=0.3, y=0.2, label = "Low Salinity") +
  annotate("rect", xmin = 0, xmax = 0.62, ymin = 0, ymax = 0.25, alpha = .1) +
  geom_smooth(method = "lm", level = 0.95, alpha = .15, aes(group=Temp,colour = factor(Temp))) +
  theme_classic() 


pd <- position_dodge(0.1) # adjust the jitter for the different treatments   
Resp_APRIL %>% 
  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                            "HHH", "HLH", "LHH",'LLH',
                            "HHL", "HLL", "LHL", 'LLL')) %>%
  summarySE(measurevar="resp_ng_L_indiv_hr", groupvars=c("full.treatment", "meanAragonite", "Temp")) %>% 
  ggplot(aes(meanAragonite, resp_ng_L_indiv_hr , group =full.treatment, fill = factor(Temp))) +     
    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.05))+
    geom_errorbar(aes(ymin=resp_ng_L_indiv_hr-se, ymax=resp_ng_L_indiv_hr+se), colour="black", width=.1, position=pd) +
    geom_line(position=pd) +
    scale_fill_manual(values=c("#D55E00","#56B4E9", "#D55E00","#56B4E9", 
                               "#D55E00","#56B4E9", "#D55E00","#56B4E9")) +
    labs(title = "Respiration rates; C virginica day 1", 
         y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
         x = "Aragonite saturation") +
    annotate("text", x=0.3, y=0.24, label = "Low Salinity") +
    annotate("text", x=1.25, y=0.24, label = "High Salinity") +
    annotate("text", x=1.58, y=0.14, label = "a") +
    annotate("text", x=1.65, y=0.018, label = "b") +
    annotate("rect", xmin = 0, xmax = 0.62, ymin = 0, ymax = 0.25, alpha = .05) +
    # geom_smooth(method = "lm", level = 0.95, alpha = .15, aes(group=Temp,colour = factor(Temp))) +
    theme_classic() 



```

### Day 8 Respirometry (20210507)
```{r day 8 analysis, echo=TRUE}

# a.
Resp_MAY <- Resp.Master %>% 
  dplyr::filter(Date %in% '5/7/2021')
# b.
Resp_MAY <- merge(Resp_MAY, aragonite_dat, by = 'TempCarbSal') # merge with the mean aragonite saturation state
# c.
LMmod.MAY   <- aov(lm(resp_ng_L_indiv_hr~Temp*pCO2*Salinity,data=Resp_MAY))
print('LM model  == aov( lm ( resp_ng_L_indiv_hr ~ Temp * pCO2 * Salinity, data = Resp_APRIL ) )')
summary(LMmod.MAY)
# check_model(LMmod.MAY) # observe the diagnostics of the model
shapiro.test(residuals(LMmod.MAY)) # non normal
leveneTest(LMmod.MAY) # good

# LME model here however we do only have one rep per chamber_tank in some cases, thus the lm (above is the same)
# MEmod.APRIL    <- lmer(resp_ng_L_indiv_hr~Temp*pCO2*Salinity + (1|Chamber_tank),REML=F, data=Resp_APRIL)
# summary(MEmod.APRIL)
# check_model(MEmod.APRIL)
# shapiro.test(residuals(MEmod.APRIL)) # non normal
# leveneTest(MEmod.APRIL) # good


# d. 
Resp_MAY_select  <- Resp_MAY %>% dplyr::select(c('resp_ng_L_indiv_hr', 'Temp', 'pCO2', 'Salinity'))
Resp_MAY_melt    <- tidyr::gather(Resp_MAY_select, variable, value, -resp_ng_L_indiv_hr)

# MAIN EFFECT PLOT
# ggplot(Resp_APRIL_melt, aes(value , resp_ng_L_indiv_hr , fill = factor(value ))) +
#   theme(panel.grid=element_blank()) +
#   scale_color_manual(values=c("#56B4E9","#D55E00")) +
#   geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.5))+
#   geom_boxplot(size=0.2, alpha=0.1) +
#   theme_bw() +
#   facet_wrap(~variable, scales = "free_y")

# INTERACTION PLOT
Resp_MAY %>%
  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                            "HHH", "HLH", "LHH",'LLH',
                            "HHL", "LHL", 'LLL')) %>%
  ggplot(aes(meanAragonite, resp_ng_L_indiv_hr , group =full.treatment, fill = factor(Temp))) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.05))+
  #geom_boxplot(size=.2, alpha=0.1, width =0.2) +
  scale_fill_manual(values=c("#D55E00","#56B4E9", "#D55E00","#56B4E9", 
                             "#D55E00","#56B4E9", "#D55E00","#56B4E9")) +
  labs(title = "Respiration rates; C virginica day 8", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
       x = "Aragonite saturation") +
  annotate("text", x=0.3, y=0.55, label = "Low Salinity") +
  annotate("rect", xmin = 0, xmax = 0.62, ymin = 0, ymax = 0.6, alpha = .1) +
  geom_smooth(method = "lm", level = 0.95, alpha = .15, aes(group=Temp,colour = factor(Temp))) +
  theme_classic() 

```