---
title: "resp_calc_analysis_RMD"
author: "Samuel Gurr"
date: "9/22/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r load packages + set wd + load data + ready data, include=FALSE}
# Purpose: Oyster project 2021 - Respiration rate data 
# analysis of respiration rate data
# Written by: Sam J Gurr (last edit 9/14/2021)

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(reshape2)
library(lme4)
library(lmerTest)
library(performance) # check check_model QC 
library(see)
library(patchwork)
library(forcats)
library(lawstat)
library(car)
library(pander)
# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

setwd("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis") # personal computer
# setwd("C:/Users/samuel.gurr/Documents/Github_repositories/Cvriginica_multistressor/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

exp_metadata <- read.csv(file="Data/ExperimentMetadata.csv", header=T) # treatment assignments to 'Chamber_Tank'

aragonite_dat<- read.csv(file='Output/Water_Chem/Chem.Table_sep.csv', header = T) %>% 
  dplyr::select(c('meanAragonite','Temp_OA_Sal')) %>%  
  dplyr::rename(TempCarbSal = Temp_OA_Sal)
aragonite_dat$TempCarbSal <-  gsub("_", "", aragonite_dat$TempCarbSal)

counts_resp  <- read.csv(file="Data/Counts_resp.csv", header=T) # reference for the respirometry data - contains the 'Chamber_Tank' for each sensor channel (whether an animal or a blank)
resp.ref     <- read.csv(file="Data/Respiration/Reference_master.csv", header=T) %>% 
  dplyr::filter(!Filename %in% c('1_3_19_21_raw.txt', 'may_7_2021_low_temo_10-12_ans_13-15_high_sal_raw_b.txt')) # reference for the respirometry data - contains the 'Chamber_Tank' for each sensor channel (whether an animal or a blank)
resp.data    <- read.csv(file="Output/Respiration/Cumulative_resp_alpha0.4.csv", header=T) %>% 
  dplyr::filter(!Filename %in% c('1_3_19_21_raw.txt', 'may_7_2021_low_temo_10-12_ans_13-15_high_sal_raw_b.txt'))# read the calculated raw rates from 'resp_LoLin' script - contains the calculated rate (not normalized for blanks) for each sensor-channel

# merge the exp_metadata with the resp.data
resp.ref_merged                 <- merge(exp_metadata, resp.ref, by = 'Chamber_tank', all=TRUE) # all TRUE allows us to keep the blanks
resp.data_merged                <- merge(resp.data, resp.ref_merged, by = c('Date', 'Channel','Notes','Filename')) %>% 
                                      dplyr::mutate(TempCarbSal = case_when( !is.na(Temp) ~ (as.character(paste(Temp, pCO2, Salinity, sep =''))) )) %>% 
                                      dplyr::mutate(Aragonite_saturation = case_when( (TempCarbSal == "HHH") ~ 0.7,
                                                                                      (TempCarbSal == 'HHL') ~ 0.3, 
                                                                                      (TempCarbSal == 'HLH') ~ 1.6,
                                                                                      (TempCarbSal == 'HLL') ~ 0.6,
                                                                                      (TempCarbSal == 'LLL') ~ 0.5,
                                                                                      (TempCarbSal == 'LLH') ~ 1.5,
                                                                                      (TempCarbSal == 'LHL') ~ 0.2,
                                                                                      (TempCarbSal == 'LHH') ~ 0.6))
```



### CALCULATE RESPIRATION RATES
(1) summary table of blanks to normalize respiration rates
  - we will use 'Lpc' value (or L%) was chosen to generally choose the local regression with the majority of observations in the truly linear subset of data
  - review Olito et al. 2017 Estimating monotonic rates from biological data using local linear regression
  
  
```{r blanks, echo=FALSE}

dates.runs <- resp.data_merged %>%  # call table
  dplyr::distinct(Date, Notes) # call all unique values for date run and sw condition
dates.runs <- na.omit(dates.runs)
# call dataframe and build table to rbind in for loop
blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Notes', 'BLANK.mean.Lpc', 'BLANK.mean.Leq' , 'BLANK.mean.Lz') # names for comuns in the for loop

# for loop. objective = obtian a mean value for all blanks specific to date, run #, seawater treatment
for(i in 1:nrow(dates.runs)) {
  data <- resp.data_merged %>% 
    dplyr::select(Date, Chamber_tank, Notes, Lpc,  Leq, Lz) %>% 
    dplyr::filter(!is.na(Lpc)) %>% # ommits empty resp channels (if any)
    dplyr::filter(Notes == dates.runs[i,2])
  
  blanks <- data %>%
    dplyr::filter(Chamber_tank == "blank") %>% 
    dplyr::summarise(mean_Lpc = mean(abs(Lpc)),
                     mean_Leq = mean(abs(Leq)), 
                     mean_Lz = mean(abs(Lz)))
  
  blanks.table$Date           <- dates.runs[i,1] # all files have date in the form of yyyymmdd at the start of each csv name
  #blanks.table$RUN <- dates.runs[i,2] # assign the run to the number in the title for the trials completed that day
  blanks.table$Notes      <- dates.runs[i,2]
  blanks.table$BLANK.mean.Lpc <- blanks[1,1]
  blanks.table$BLANK.mean.Leq <- blanks[1,2]
  blanks.table$BLANK.mean.Lz  <- blanks[1,3]
  # blanks.table$alpha <- data[1,9] # set at start of script - reresents the proportion of data for final estimate of slopes (Lpc, Leq, Lz)
  
  df <- data.frame(blanks.table) # name dataframe for this singl e row
  blanks_total <- rbind(blanks_total,df) #bind to a cumulative list dataframe
  # print(blanks_total) # print to monitor progress
}

head(blanks_total) # view blanks table
```



(2) Calculate respiration rates as ng O2 L-1 indiv-1 hr-1
  - normalize by mean value of blanks for each treatment, grouped by 'Date' and 'Notes' (as the run wihtin day)
  - omit rows resprenting blank resp > sample resp - likely bad data, view to troubleshoot if needed
  
  
```{r normalize resp rates by blanks, echo=FALSE}
Resp.blanks.merge <- merge(resp.data_merged, blanks_total, by=c("Date", "Notes")) %>% # NOTE: this repeats for every distinct length value
  dplyr::filter(!Chamber_tank =='blank') %>% 
  dplyr::filter(!Lpc > 0) %>% # onlynegative raw lpc values from LoLinR represent oxygen depletion - positive values are errors
  dplyr::mutate(resp_norm = abs(Lpc) - BLANK.mean.Lpc)   #  Lpc is still raw data (take abs) then resp - blank,


Resp.blanks.merge_OM <- Resp.blanks.merge %>% dplyr::filter(resp_norm > 0)  # omits respiration rate values LESS than the blank (resp_norm < 0)
Resp.outliers        <- Resp.blanks.merge %>% dplyr::filter(resp_norm < 0)  # 10 total samples lower than the blank  
print(c("number of blank resp > sample resp =",nrow(Resp.outliers)))

count_check_all <- Resp.blanks.merge_OM %>% dplyr::group_by(Date,TempCarbSal) %>% dplyr::summarise(n = n())
knitr::kable(count_check_all)

count_check_true_rates <- Resp.blanks.merge_OM %>% dplyr::filter(!Lpc > 0) %>% dplyr::group_by(Date,TempCarbSal) %>% dplyr::summarise(n = n()) # omit those wit positive values - no oxygen consumption recorded 
knitr::kable(count_check_true_rates)
### no HLL after filtered of poor data
```

- calculate resp rates
  
```{r calc as resp_ng_L_indiv_hr, echo=FALSE}
vial.vol <- 0.08 # milliliters (ml)
Resp.Master <- merge(Resp.blanks.merge_OM[,c(1,3,5,9:14,18)], counts_resp[,c(1,6:7)], by = c('Date','Chamber_tank'))
Resp.Master$resp_ng_L_indiv_hr <- ( 
                                    ( ( (abs(Resp.Master$resp_norm)*1000000) * # call absolute value of resp in mg per minute - convert to ng min-1
                                        (vial.vol/1000) ) / # correct ng minute-1 to ng liter-1 by multiplying by the resp vial in liters
                                        Resp.Master$Counts ) * # normalize by individual or larvae count - as to ng L-1 individual-1
                                      (60)) # correct for the time; final value is ng Liter-1 individual-1 hour-1

# mean sd rates
# mean(Resp.Master$resp_ng_L_indiv_hr) # mean = 0.4994656
# sd(Resp.Master$resp_ng_L_indiv_hr) # sd= 0.8197345

Resp.Master[,c(1:3,12)]
```


## ANALYSIS
### Day 1 Respirometry (20210430)
  - a. filter the dataset for target data
  - b. add column for mean aragonite sat. (note: this is from the entire experiment, not just day 1 chemistry!)
  - c. run moels and diagnostics
  - d. plot (reconfigure data as needed for plotting; i.e. melt/dcast, etc.)
  
  
```{r RESP Age 24 hours - all data, echo=TRUE}

# a.
Resp_age1 <- Resp.Master %>% 
  dplyr::filter(Date %in% '4/30/2021')  %>% 
  dplyr::mutate(Treatment = as.character(paste('Temp.', Temp, '_OA.', pCO2, '_Sal.',Salinity, sep = ''))) %>% 
  dplyr::mutate(pCO2_Salinity = as.character(substr(TempCarbSal, 2, 3))) %>% 
  dplyr::mutate(Temp = (fct_relevel(Temp, c('L','H'))))

# b.
Resp_age1 <- merge(Resp_age1, aragonite_dat, by = 'TempCarbSal') # merge with the mean aragonite saturation state

## Plot geeom boxlot with jitter
Resp_Age1_Boxplot <- ggplot(data=Resp_age1, 
                            aes(x=as.factor(Aragonite_saturation), 
                            #aes(x=meanAragonite, 
                                y=resp_ng_L_indiv_hr, 
                                fill=pCO2_Salinity)) +
                            geom_boxplot()+
                            geom_jitter(width = 0.1)+
                            scale_fill_manual(values=c("skyblue2", "darkorange3","royalblue3", "orange2"))+
                            theme_bw() +  
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
                            theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
                            labs(title = "Age =24 hours; Respiration rates", 
                                   y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
                                   x = "Aragonite saturation") +
                            theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
                            theme(axis.text=element_text(size=12)) + 
                            facet_wrap(~Temp )
Resp_Age1_Boxplot


# c.
LMmod.age1   <- aov(lm( resp_ng_L_indiv_hr~Temp*pCO2*Salinity,data=Resp_age1))
print('LM model  == aov( lm ( resp_ng_L_indiv_hr ~ Temp * pCO2 * Salinity, data = Resp_APRIL ) )')
pander(anova(LMmod.age1), style='rmarkdown') # anova table of lmer
# |         &nbsp;         | Df |  Sum Sq   |  Mean Sq  | F value | Pr(>F)  |
# |:----------------------:|:--:|:---------:|:---------:|:-------:|:-------:|
# |        **Temp**        | 1  |  0.01558  |  0.01558  |  5.849  | 0.02788 |
# |        **pCO2**        | 1  | 0.0007855 | 0.0007855 | 0.2948  | 0.5946  |
# |      **Salinity**      | 1  | 0.001727  | 0.001727  | 0.6482  | 0.4326  |
# |     **Temp:pCO2**      | 1  |  0.01284  |  0.01284  |  4.817  | 0.04328 |
# |   **Temp:Salinity**    | 1  | 0.0001993 | 0.0001993 | 0.07478 |  0.788  |
# |   **pCO2:Salinity**    | 1  | 0.0007812 | 0.0007812 | 0.2932  | 0.5956  |
# | **Temp:pCO2:Salinity** | 1  | 0.000818  | 0.000818  |  0.307  | 0.5872  |
# |     **Residuals**      | 16 |  0.04263  | 0.002664  |   NA    |   NA    |

check_model(LMmod.age1) # observe the diagnostics of the model
shapiro.test(residuals(LMmod.age1)) # 0.0107 non normal
leveneTest(LMmod.age1) # 0.3331 good

# POst-hoc tests and exploration of sig effects
TukeyHSD(LMmod.age1, 'Temp:pCO2')


# d. 
Resp_age1_select  <- Resp_age1 %>% dplyr::select(c('resp_ng_L_indiv_hr', 'Temp', 'pCO2', 'Salinity', 'Aragonite_saturation'))
Resp_age1L_melt    <- tidyr::gather(Resp_age1_select, variable, value, -resp_ng_L_indiv_hr)

# MAIN EFFECT PLOT
# ggplot(Resp_APRIL_melt, aes(value , resp_ng_L_indiv_hr , fill = factor(value ))) +
#   theme(panel.grid=element_blank()) +
#   scale_color_manual(values=c("#56B4E9","#D55E00")) +
#   geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.5))+
#   geom_boxplot(size=0.2, alpha=0.1) +
#   theme_bw() +
#   facet_wrap(~variable, scales = "free_y")

# INTERACTION PLOT
Resp_age1 %>%
  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                            "HHH", "HLH", "LHH",'LLH',
                            "HHL", "HLL", "LHL", 'LLL')) %>%
  ggplot(aes(meanAragonite, resp_ng_L_indiv_hr , group =full.treatment, fill = factor(Temp))) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.05))+
  #geom_boxplot(size=.2, alpha=0.1, width =0.2) +
  scale_fill_manual(values=c("#D55E00","#56B4E9", "#D55E00","#56B4E9", 
                             "#D55E00","#56B4E9", "#D55E00","#56B4E9")) +
  labs(title = "Respiration rates; C virginica day 1", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
       x = "Aragonite saturation") +
  annotate("text", x=0.3, y=0.2, label = "Low Salinity") +
  annotate("rect", xmin = 0, xmax = 0.62, ymin = 0, ymax = 0.25, alpha = .1) +
  geom_smooth(method = "lm", level = 0.95, alpha = .15, aes(group=Temp,colour = factor(Temp))) +
  theme_classic() 


pd <- position_dodge(0.1) # adjust the jitter for the different treatments   
library(Rmisc)
Resp_age1 %>% 
  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                            "HHH", "HLH", "LHH",'LLH',
                            "HHL", "HLL", "LHL", 'LLL')) %>%
  summarySE(measurevar="resp_ng_L_indiv_hr", groupvars=c("full.treatment", "meanAragonite", "Temp")) %>% 
  ggplot(aes(meanAragonite, resp_ng_L_indiv_hr , group =full.treatment, fill = factor(Temp))) +     
    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.05))+
    geom_errorbar(aes(ymin=resp_ng_L_indiv_hr-se, ymax=resp_ng_L_indiv_hr+se), colour="black", width=.1, position=pd) +
    geom_line(position=pd) +
    scale_fill_manual(values=c("#D55E00","#56B4E9", "#D55E00","#56B4E9", 
                               "#D55E00","#56B4E9", "#D55E00","#56B4E9")) +
    labs(title = "Respiration rates; C virginica day 1", 
         y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
         x = "Aragonite saturation") +
    annotate("text", x=0.3, y=0.24, label = "Low Salinity") +
    annotate("text", x=1.25, y=0.24, label = "High Salinity") +
    annotate("text", x=1.58, y=0.14, label = "a") +
    annotate("text", x=1.65, y=0.018, label = "b") +
    annotate("rect", xmin = 0, xmax = 0.62, ymin = 0, ymax = 0.25, alpha = .05) +
    # geom_smooth(method = "lm", level = 0.95, alpha = .15, aes(group=Temp,colour = factor(Temp))) +
    theme_classic() 



```






```{r RESP Age 24 hours - HIGH TEMP ONLY, echo=TRUE}

# a.
Resp_age1_hightemp <- Resp.Master %>% 
  dplyr::filter(Date %in% '4/30/2021')  %>% 
  dplyr::filter(Temp %in% 'H') %>% 
  dplyr::mutate(Treatment = as.character(paste('OA.', pCO2, '_Sal.',Salinity, sep = ''))) %>% 
  dplyr::mutate(pCO2_Salinity = as.character(substr(TempCarbSal, 2, 3)))

# b.
Resp_age1_hightemp <- merge(Resp_age1_hightemp, aragonite_dat, by = 'TempCarbSal') # merge with the mean aragonite saturation state

## Plot geeom boxlot with jitter
Resp_Age1_Boxplot_hightemp <- ggplot(data=Resp_age1_hightemp, 
                                  aes(x=as.factor(Aragonite_saturation), 
                                  #aes(x=meanAragonite, 
                                      y=resp_ng_L_indiv_hr, 
                                      fill=pCO2_Salinity)) +
                                  geom_boxplot()+
                                  geom_jitter(width = 0.1)+
                                  scale_fill_manual(values=c("skyblue2", "darkorange3","royalblue3", "orange2"))+
                                  theme_bw() +  
                                  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
                                  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
                                  labs(title = "Age =24 hours; Respiration rates", 
                                         y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
                                         x = "Aragonite saturation") +
                                  theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
                                  theme(axis.text=element_text(size=12)) 
Resp_Age1_Boxplot_hightemp


# c. two way anova model (pcO2 * salinity)

LMmod.age1_hightemp   <- aov(lm( log(resp_ng_L_indiv_hr)~pCO2*Salinity,data=Resp_age1_hightemp))
print('LM model  == aov( lm ( resp_ng_L_indiv_hr ~ pCO2 * Salinity, data = Resp_APRIL ) )')
pander(anova(LMmod.age1_hightemp), style='rmarkdown') # anova table of lmer
# |      &nbsp;       | Df |  Sum Sq  | Mean Sq  | F value | Pr(>F) |
# |:-----------------:|:--:|:--------:|:--------:|:-------:|:------:|
# |     **pCO2**      | 1  | 0.003635 | 0.003635 |  2.763  | 0.135  |
# |   **Salinity**    | 1  | 0.00155  | 0.00155  |  1.178  | 0.3094 |
# | **pCO2:Salinity** | 1  | 0.001599 | 0.001599 |  1.215  | 0.3023 |
# |   **Residuals**   | 8  | 0.01052  | 0.001316 |   NA    |   NA   |
check_model(LMmod.age1_hightemp) # observe the diagnostics of the model
shapiro.test(residuals(LMmod.age1_hightemp)) # 0.001365 non normal
leveneTest(LMmod.age1_hightemp) # 0.3834 good



# c.2 ommit the high outlier resp value (> 0.14)
Resp_age1_hightempOM   <- Resp_age1_hightemp %>% dplyr::filter(!resp_ng_L_indiv_hr > 0.14) # ommit the outlier at ~ 0.15

LMmod.age1_hightempOM  <- aov(lm( log(resp_ng_L_indiv_hr)~pCO2*Salinity,data=Resp_age1_hightempOM))
print('LM model  == aov( lm ( resp_ng_L_indiv_hr ~ pCO2 * Salinity, data = Resp_APRIL ) )')
pander(anova(LMmod.age1_hightempOM), style='rmarkdown') # anova table of lmer
# |      &nbsp;       | Df |  Sum Sq  | Mean Sq  | F value | Pr(>F)  |
# |:-----------------:|:--:|:--------:|:--------:|:-------:|:-------:|
# |     **pCO2**      | 1  |  3.432   |  3.432   |  32.13  | 0.00076 |
# |   **Salinity**    | 1  | 0.009019 | 0.009019 | 0.08443 | 0.7798  |
# | **pCO2:Salinity** | 1  |  0.0363  |  0.0363  | 0.3399  | 0.5782  |
# |   **Residuals**   | 7  |  0.7477  |  0.1068  |   NA    |   NA    |
check_model(LMmod.age1_hightempOM) # observe the diagnostics of the model
shapiro.test(residuals(LMmod.age1_hightempOM)) # 0.3748  normal
leveneTest(LMmod.age1_hightempOM) # 0.915 good



# NOTE: log transformation also resolves normality w/o transformtion - also yields significant effect of pCO2 treatment is same directionality




# d. plot the high temp resp dat (with outlier ommitted - pCO2 effect!)


Age24hrs_Resp_hightemp.Box <- ggplot(data=Resp_age1_hightempOM, aes(x=fct_relevel(pCO2, c("L", "H")), 
                                        y=resp_ng_L_indiv_hr, 
                                        colour=fct_relevel(Salinity, c("L", "H")))) +
                                          geom_boxplot() + 
                                          theme_classic() +  
                                          geom_jitter(width = 0.1)+
                                          ylim(0,0.03) +
                                          stat_summary(fun.y="mean",position = position_dodge2(width = 0.75)) +
                                          theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
                                          theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
                                          labs(title="Age = 24 hours (high temp only)", 
                                               x ="pCO2 level", 
                                               y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")")) + 
                                          theme(axis.title.y = element_text(size = rel(1.3), angle =90), 
                                                axis.title.x = element_text(size = rel(1.3), angle = 0)) +
                                          theme(axis.text=element_text(size=12)) 

Age24hrs_Resp_hightemp.MEANSE <- Resp_age1_hightempOM %>% 
                                    dplyr::group_by(pCO2,Salinity) %>% 
                                    dplyr::summarise(mean_resp = mean(resp_ng_L_indiv_hr), 
                                                     n         = n(),
                                                     sd_resp   = sd(resp_ng_L_indiv_hr),
                                                     se_resp   = sd_resp/(sqrt(n))) %>% 
                                        ggplot(aes(x=fct_relevel(pCO2, c("L", "H")), 
                                                                       y=mean_resp, 
                                                                       colour=fct_relevel(Salinity, c("L", "H")))) + 
                                                                      # linetype = Temp)) +
                                        geom_point(aes (colour = fct_relevel(Salinity, c("L", "H"))), position = "dodge2") +
                                        geom_errorbar(aes(ymin = mean_resp - se_resp, ymax = mean_resp + se_resp), width = 0.5, position= "dodge2") +
                                        theme_classic() +  
                                        ylim(0,0.03) +
                                        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
                                        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
                                        labs(title="Age = 24 hours (high temp only)", 
                                             x ="pCO2 level", 
                                             y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"))+ 
                                        theme(axis.title.y = element_text(size = rel(1.3), 
                                                                          angle =90), 
                                                                          axis.title.x = element_text(size = rel(1.3), 
                                                                          angle = 0)) +
                                theme(axis.text=element_text(size=12)) 
#print
library(ggpubr)
setwd("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis")
pdf("Output/Respiration/Respiration_age_24hrs_MeanSE_hightemp.pdf", width=14, height=6)
print(ggarrange(Age24hrs_Resp_hightemp.MEANSE,Age24hrs_Resp_hightemp.Box))
dev.off()





# d. 
Resp_age1_select_hightempOM   <- Resp_age1_hightempOM %>% dplyr::select(c('resp_ng_L_indiv_hr', 'pCO2', 'Salinity', 'Aragonite_saturation'))
Resp_age1L_melt_hightempOM    <- tidyr::gather(Resp_age1_select_hightempOM, variable, value, -resp_ng_L_indiv_hr)

# MAIN EFFECT PLOT
Age24hrs_Resp_effect_plots <- ggplot(Resp_age1L_melt_hightempOM, aes(value , resp_ng_L_indiv_hr , fill = factor(value ))) +
                    theme(panel.grid=element_blank()) +
                    scale_color_manual(values=c("#56B4E9","#D55E00")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.5))+
                    geom_boxplot(size=0.2, alpha=0.1) +
                    theme_bw() +
                    facet_wrap(~variable, scales = "free_y")

setwd("C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis")
pdf("Output/Respiration/Respiration_age_24hrs_boxplots_hightemp.pdf", width=14, height=6)
print(Age24hrs_Resp_effect_plots)
dev.off()


```







### Day 8 Respirometry (20210507)
```{r day 8 analysis, echo=TRUE}

# a.
Resp_age8 <- Resp.Master %>% 
  dplyr::filter(Date %in% '5/7/2021') %>% 
  dplyr::mutate(Treatment = as.character(paste('Temp.', Temp, '_OA.', pCO2, '_Sal.',Salinity, sep = ''))) %>% 
  dplyr::mutate(pCO2_Salinity = as.character(substr(TempCarbSal, 2, 3))) %>% 
  dplyr::mutate(Temp = (fct_relevel(Temp, c('L','H'))))

# b.
Resp_age8 <- merge(Resp_age8, aragonite_dat, by = 'TempCarbSal') # merge with the mean aragonite saturation state


## Plot geeom boxlot with jitter
Resp_Age8_Boxplot <- ggplot(data=Resp_age8, 
                            aes(x=as.factor(Aragonite_saturation), 
                            #aes(x=meanAragonite, 
                                y=resp_ng_L_indiv_hr, 
                                fill=pCO2_Salinity)) +
                            geom_boxplot()+
                            geom_jitter(width = 0.1)+
                            scale_fill_manual(values=c("skyblue2", "darkorange3","royalblue3", "orange2"))+
                            theme_bw() +  
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
                            theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
                            labs(title = "Age = 8 days; Respiration rates", 
                                   y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
                                   x = "Aragonite saturation") +
                            theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
                            theme(axis.text=element_text(size=12)) + 
                            facet_wrap(~Temp )
Resp_Age8_Boxplot


# c.
LMmod.age8   <- aov(lm(resp_ng_L_indiv_hr~Temp*pCO2*Salinity,data=Resp_age8))
print('LM model  == aov( lm ( resp_ng_L_indiv_hr ~ Temp * pCO2 * Salinity, data = Resp_APRIL ) )')
summary(LMmod.age8)
# check_model(LMmod.age8) # observe the diagnostics of the model
shapiro.test(residuals(LMmod.age8)) # non normal
leveneTest(LMmod.age8) # good

# LME model here however we do only have one rep per chamber_tank in some cases, thus the lm (above is the same)
# MEmod.APRIL    <- lmer(resp_ng_L_indiv_hr~Temp*pCO2*Salinity + (1|Chamber_tank),REML=F, data=Resp_APRIL)
# summary(MEmod.APRIL)
# check_model(MEmod.APRIL)
# shapiro.test(residuals(MEmod.APRIL)) # non normal
# leveneTest(MEmod.APRIL) # good


# d. 
Resp_age8_select  <- Resp_age8 %>% dplyr::select(c('resp_ng_L_indiv_hr', 'Temp', 'pCO2', 'Salinity'))
Resp_age8_melt    <- tidyr::gather(Resp_age8_select, variable, value, -resp_ng_L_indiv_hr)

# MAIN EFFECT PLOT
# ggplot(Resp_APRIL_melt, aes(value , resp_ng_L_indiv_hr , fill = factor(value ))) +
#   theme(panel.grid=element_blank()) +
#   scale_color_manual(values=c("#56B4E9","#D55E00")) +
#   geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.5))+
#   geom_boxplot(size=0.2, alpha=0.1) +
#   theme_bw() +
#   facet_wrap(~variable, scales = "free_y")

# INTERACTION PLOT
Resp_age8 %>%
  dplyr::mutate(full.treatment = (paste(Temp, pCO2, Salinity,sep=''))) %>%
  dplyr::mutate(full.treatment = fct_relevel(full.treatment,
                            "HHH", "HLH", "LHH",'LLH',
                            "HHL", "LHL", 'LLL')) %>%
  ggplot(aes(meanAragonite, resp_ng_L_indiv_hr , group =full.treatment, fill = factor(Temp))) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.05))+
  #geom_boxplot(size=.2, alpha=0.1, width =0.2) +
  scale_fill_manual(values=c("#D55E00","#56B4E9", "#D55E00","#56B4E9", 
                             "#D55E00","#56B4E9", "#D55E00","#56B4E9")) +
  labs(title = "Respiration rates; C virginica day 8", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%indiv^{-1}%.% hr^{-1}~")"), 
       x = "Aragonite saturation") +
  annotate("text", x=0.3, y=0.55, label = "Low Salinity") +
  annotate("rect", xmin = 0, xmax = 0.62, ymin = 0, ymax = 0.6, alpha = .1) +
  geom_smooth(method = "lm", level = 0.95, alpha = .15, aes(group=Temp,colour = factor(Temp))) +
  theme_classic() 

```